\documentclass{Configuration_Files/PoliMi3i_thesis}

%------------------------------------------------------------------------------
%	REQUIRED PACKAGES AND  CONFIGURATIONS
%------------------------------------------------------------------------------

% CONFIGURATIONS
\usepackage{parskip} % For paragraph layout
\usepackage{setspace} % For using single or double spacing
\usepackage{emptypage} % To insert empty pages
\usepackage{multicol} % To write in multiple columns (executive summary)
\usepackage{minted}
\setlength\columnsep{15pt} % Column separation in executive summary
\setlength\parindent{0pt} % Indentation
\raggedbottom  

% PACKAGES FOR TITLES
\usepackage{titlesec}
% \titlespacing{\section}{left spacing}{before spacing}{after spacing}
\titlespacing{\section}{0pt}{3.3ex}{2ex}
\titlespacing{\subsection}{0pt}{3.3ex}{1.65ex}
\titlespacing{\subsubsection}{0pt}{3.3ex}{1ex}
\usepackage{color}

% PACKAGES FOR LANGUAGE AND FONT
\usepackage[english]{babel} % The document is in English  
\usepackage[utf8]{inputenc} % UTF8 encoding
\usepackage[T1]{fontenc} % Font encoding
\usepackage[11pt]{moresize} % Big fonts

% PACKAGES FOR IMAGES
\usepackage{graphicx}
\usepackage{transparent} % Enables transparent images
\usepackage{eso-pic} % For the background picture on the title page
\usepackage{subfig} % Numbered and caption subfigures using \subfloat.
\usepackage{tikz} % A package for high-quality hand-made figures.
\usetikzlibrary{}
\graphicspath{{./Images/}} % Directory of the images
\usepackage{caption} % Coloured captions
\usepackage{xcolor} % Coloured captions
\usepackage{amsthm,thmtools,xcolor} % Coloured "Theorem"
\usepackage{float}

% STANDARD MATH PACKAGES
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage[overload]{empheq} % For braced-style systems of equations.
\usepackage{fix-cm} % To override original LaTeX restrictions on sizes

% PACKAGES FOR TABLES
\usepackage{tabularx}
\usepackage{longtable} % Tables that can span several pages
\usepackage{colortbl}

% PACKAGES FOR ALGORITHMS (PSEUDO-CODE)
\usepackage{algorithm}
\usepackage{algorithmic}

% PACKAGES FOR REFERENCES & BIBLIOGRAPHY
\usepackage[colorlinks=true,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=black]{hyperref} % Adds clickable links at references
\usepackage{cleveref}
\usepackage[square, numbers, sort&compress]{natbib} % Square brackets, citing references with numbers, citations sorted by appearance in the text and compressed
\bibliographystyle{abbrvnat} % You may use a different style adapted to your field

% OTHER PACKAGES
\usepackage{pdfpages} % To include a pdf file
\usepackage{afterpage}
\usepackage{lipsum} % DUMMY PACKAGE
\usepackage{fancyhdr} % For the headers
\fancyhf{}

% Input of configuration file. Do not change config.tex file unless you really know what you are doing. 
\input{Configuration_Files/config}

%----------------------------------------------------------------------------
%	NEW COMMANDS DEFINED
%----------------------------------------------------------------------------

% EXAMPLES OF NEW COMMANDS
\newcommand{\bea}{\begin{eqnarray}} % Shortcut for equation arrays
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\e}[1]{\times 10^{#1}}  % Powers of 10 notation

%----------------------------------------------------------------------------
%	ADD YOUR PACKAGES (be careful of package interaction)
%----------------------------------------------------------------------------

%----------------------------------------------------------------------------
%	ADD YOUR DEFINITIONS AND COMMANDS (be careful of existing commands)
%----------------------------------------------------------------------------

%----------------------------------------------------------------------------
%	BEGIN OF YOUR DOCUMENT
%----------------------------------------------------------------------------

\begin{document}

\fancypagestyle{plain}{%
\fancyhf{} % Clear all header and footer fields
\fancyhead[RO,RE]{\thepage} %RO=right odd, RE=right even
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}}

%----------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------

\pagestyle{empty} % No page numbers
\frontmatter % Use roman page numbering style (i, ii, iii, iv...) for the preamble pages

\puttitle{
	title=Implementation of a Key Management Entity for Quantum Key Distribution, % Title of the thesis
	name=Nicolò Sala, % Author Name and Surname
	course=Computer Science Engineering - Ingegneria Informatica, % Study Programme (in Italian)
	ID  = 945898,  % Student ID number (numero di matricola)
	advisor= Prof. Paolo Martelli, % Supervisor name
	coadvisor={Alberto Gatto, Marco Brunero}, % Co-Supervisor name, remove this line if there is none
	academicyear={2021-22},  % Academic Year
} % These info will be put into your Title page 

%----------------------------------------------------------------------------
%	PREAMBLE PAGES: ABSTRACT (inglese e italiano), EXECUTIVE SUMMARY
%----------------------------------------------------------------------------
\startpreamble
\setcounter{page}{1} % Set page counter to 1

% ABSTRACT IN ENGLISH
\chapter*{Abstract} 
The Internet requires the ability to exchange secret keys through a public communication channel. Each key is then used to encrypt confidential messages between two entities.

The current protocols for exchanging secret keys are based on mathematical problems that are extremely hard to solve, requiring a time of computation too long also for the most powerful today's classical computer.

However, the development of quantum computers will soon make it easy to tackle such problems, resulting in a lack of security in our communications.

Today's most promising solution is Quantum Key Distribution (QKD). It allows unconditional secure sharing of secrets based on quantum mechanics' fundamental principles.

The secret bit sequences produced through QKD have a length that cannot be determined a priori, while applications often need a key with a predetermined length. Furthermore, once produced via QKD, the bit sequence must be made available to applications in an equally secure manner.

This document describes the implementation of a Key Management Entity (KME), the software dedicated to creating secret keys of fixed length, starting from the bits shared securely through QKD.

After describing the evolution of the problem of sharing secrets in a public channel showing QKD as a solution, we move on to the description of how KME works. After that, the details of the proposed implementation are analyzed to finally arrive at the interaction of the KME with currently available quantum modules.


\textbf{Keywords}: Quantum Key Distribution, Key Management Entity

% ABSTRACT IN ITALIAN
\chapter*{Abstract in lingua italiana}
Internet richiede la capacità di scambiare chiavi segrete attraverso un canale di comunicazione pubblico. Ogni chiave è poi utilizzata per cifrare messaggi confidenziali tra due entità.

Gli attuali protocolli informatici per lo scambio di chiavi segrete sono basati su problemi di matematica molto difficili da risolvere, poiché richiedono un tempo di elaborazione troppo lungo anche per il computer elettronico più potente ad oggi.

Tuttavia, lo sviluppo di computer quantistici renderà presto semplice la risoluzione di tali problemi, portando di conseguenza a una mancanza di sicurezza nelle nostre comunicazioni.

La soluzione più promettente al giorno d'oggi è la Quantum Key Distribution (QKD), la quale consente di condividere segreti in modo incondizionatamente sicuro, basandosi sui principi fondamentali della meccanica quantistica.

Le sequenze di bit segrete prodotte attraverso QKD hanno una lunghezza non determinabile a priori, mentre le applicazioni spesso necessitano di una chiave di lunghezza prefissata. Inoltre, la sequenza di bit, una volta prodotta tramite QKD, deve essere messa a disposizione delle applicazioni in maniera altrettanto sicura.

Questo documento descrive l'implementazione di una Key Management Entity (KME), il software dedito alla creazione di chiavi segrete di lunghezza fissata, a partire dai bit condivisi in maniera sicura tramite QKD.

Dopo aver descritto l'evoluzione del problema di condivisione di segreti in un canale pubblico, mostrando QKD come soluzione, si passa alla descrizione del funzionamento della KME. Dopodiché, si analizzano i dettagli dell'implementazione proposta, per giungere infine all'interazione della KME con moduli quantistici attualmente disponibili.

\textbf{Parole chiave}: Quantum Key Distribution, Key Management Entity

%----------------------------------------------------------------------------
%	LIST OF CONTENTS/FIGURES/TABLES/SYMBOLS
%----------------------------------------------------------------------------

% TABLE OF CONTENTS
\thispagestyle{empty}
\tableofcontents % Table of contents 
\thispagestyle{empty}
\cleardoublepage

%-------------------------------------------------------------------------
%	THESIS MAIN TEXT
%-------------------------------------------------------------------------
% In the main text of your thesis you can write the chapters in two different ways:
%
%(1) As presented in this template you can write:
%    \chapter{Title of the chapter}
%    *body of the chapter*
%
%(2) You can write your chapter in a separated .tex file and then include it in the main file with the following command:
%    \chapter{Title of the chapter}
%    \input{chapter_file.tex}
%
% Especially for long thesis, we recommend you the second option.

\addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics
\mainmatter % Begin numeric (1,2,3...) page numbering

% --------------------------------------------------------------------------
% NUMBERED CHAPTERS % Regular chapters following
% --------------------------------------------------------------------------

\chapter*{Introduction}
In cryptography, a private communication between two parties starts with the exchange of a shared secret, called \textit{key}. The parties may then exploit the key for encrypting messages.

If only the two parties do know the key, then the communication is said to be confidential.

Historically, sharing a secret key has been a problem: whoever listened to the communication of the private key then knew that key.

In 1976, Diffie and Hellman invented a method to exchange a secret key over a public channel. If an unwanted user listened to all the messages exchanged within the communication, they would still be unable to obtain the shared secret key.

The security of the Diffie-Hellman algorithm relies on a mathematical problem considered computationally hard: a classical computer with a finite amount of memory should not be able to solve this problem in a reasonable amount of time.

However, Quantum Cryptanalysis now threatens the computational hardness of such a mathematical problem.

In 1994, Peter Shor designed an efficient quantum algorithm that might easily compromise the security of the DH key exchange protocol.
Such an algorithm can be executed only by a quantum computer, a machine whose internal functioning is based on the laws of quantum physics.

Although none have yet implemented quantum computers capable of executing Shor's algorithm, small quantum computers are now available and working. It is a common thought that quantum computers will be able to solve computationally challenging mathematical problems in the next few years.

Therefore, researchers started looking for quantum-safe algorithms that are secure against cryptanalytic attacks by a quantum computer.

The most promising solution is Quantum Key Distribution (QKD). Thanks to the fundamental laws of quantum physics, this algorithm provides information-theoretic security, the ability to resist any attack by a quantum or classical computer with unlimited memory and time.

QKD has been implemented, and also the Politecnico di Milano has two quantum modules able to share a secret key with Quantum Key Distribution. A couple of modules able to exchange keys exploiting the QKD algorithm is called Quantum Channel.

Therefore, right now, we know a way to create secret keys confidentially. But, then, we have to think about how to manage these private keys: how do we send them to applications interested in exploiting them? How do we communicate the same secret key to different applications that want to share that private key? These and some other problems are managed by Key Management Entity software.

This document focuses on the implementation of a Key Management Entity.

After exposing the key-exchange problem in depth in chapter 1, chapter 2 describes the functionalities of a Key Management Entity, alongside the standards and conventions that have been exploited to implement the KME. Then, in chapter 3, the details of the implementation of the KME are finally shown. Next, chapter 4 describes some simulations made in Politecnico di Milano exploiting a quantum channel and our KME software. Finally, in chapter 5, we discuss the future development of the KME.


\input{Chapters/chapter_1.tex}
\input{Chapters/chapter_2.tex}
\input{Chapters/chapter_3.tex}
\input{Chapters/chapter_4.tex}
\input{Chapters/chapter_5.tex}

%-------------------------------------------------------------------------
%	BIBLIOGRAPHY
%-------------------------------------------------------------------------

\addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics
\bibliography{bibliography} % The references information are stored in the file named "bibliography.bib"

%-------------------------------------------------------------------------
%	APPENDICES
%-------------------------------------------------------------------------

\cleardoublepage
\addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics
\appendix

% LIST OF FIGURES
\listoffigures

\cleardoublepage

\end{document}
